Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary

### 2020-09-12 scripts/MouseSexDiffVar_Sept_2020.Rmd
latest 05/2020 wouldn't run / knit, seems like issues between version / rbind didn't work, reverted to bind_rows

---
title: 'Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary
  and statistical implications'
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair Senior,
  Daniel Noble, & Shinichi Nakagawa
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '4'
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
  word_document:
    toc: yes
    toc_depth: '4'
  html_notebook:
    toc: yes
  bookdown::html_document2:
    code_folding: hide
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 6
    toc_float: yes
  bookdown::word_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
subtitle: Electronic Supplementary Material
always_allow_html: yes
---

@@

                    I2_tot <- round(sum(sigma2) / sum(sigma2 + sigmaM), digits = 3)*100
                  return(I2_tot)
      }

      results_alltraits_grouping[t, c(2:17,19:26)] <- c(f(cvr),lnCVR_I2 = extract_I2(cvr), f(cv), lnVR_I2 = extract_I2(cv), f(means), lnRR_I2 = extract_I2(means), k=means$k, male_N = sum(results$male_n_ind), female_N = sum(results$female_n_ind), min_male_N = min(results$male_n_ind), max_male_N = max(results$male_n_ind), mean_male_N = mean(results$male_n_ind),
                                                        min_female_N = min(results$female_n_ind), max_female_N = max(results$female_n_ind), mean_female_N = mean(results$female_n_ind))
      results_alltraits_grouping[t, 18]   <- unique(results$trait)
    },
    error = function(e) {
      cat("ERROR :", t, conditionMessage(e), "\n")
    }
  )
}

@@

```{r cleanMeta1, results='hide'}
results_alltraits_grouping2 <- 
  results_alltraits_grouping %>%

@@

overall2 <- rbind(extract_trait(overall1, "Behaviour"), 
                      extract_trait(overall1, "Morphology"), 
                      extract_trait(overall1, "Metabolism"), 
                      extract_trait(overall1, "Physiology"), 
                      extract_trait(overall1, "Immunology"), 
                      extract_trait(overall1, "Hematology"), 
                      extract_trait(overall1, "Heart"), 
                      extract_trait(overall1, "Hearing"), 
                      extract_trait(overall1, "Eye"), 
                      All)

@@

# Invidual table for heterogeneity across all traits
# kable(metacombohetero,, digits = 3) %>%
 # kable_styling() %>%
  #scroll_box(width = "100%", height = "200px")

@@

heterog4 <- rbind(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

plot3.male.meta.CVR.b <- rbind(plot3.male.meta.CVR.b, add.row.hearing)

@@

overall4.male.sig <- rbind(lnCVR.ci, lnRR.ci) %>% 

@@

plot3.female.meta.CVR.b <- rbind(plot3.female.meta.CVR.b, add.row.hearing)

@@

overall4.female.sig <- rbind(lnCVR.ci, lnRR.ci) %>% 

@@

overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

overall4.female.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
overall4.female.sigS <- overall4.female.sigS %>%
                          mutate(value = as.numeric(value),
                                 ci.low = as.numeric(ci.low),
                                 ci.high = as.numeric(ci.low))
overall4.female.sigS$label <- "CI not overlapping zero"

@@

overall4.perc <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% 
                      select(GroupingTerm, parameter, value, ci.low, ci.high) %>%
                      mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))

@@

overall4.male.perc <- rbind(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

```{r Table1_prep, echo = FALSE, eval = TRUE, results='hide'}
  # Initial checks
  length(unique(data$parameter_name)) # 232 traits
  length(unique(data$parameter_group)) # 161 parameter groups
  length(unique(data$procedure_name)) # 26 procedure groups
  length(unique(data$biological_sample_id)) # 27147 individial mice  
  # To show a table with number of males and females per strain per production center:
     ST1 <- cbind(data %>% 
                   group_by(production_center, strain_name) %>% 
                   count(biological_sample_id, sex) %>% 
                   count(sex) %>% 
                   print(n = Inf))

```
```{r Table1, message=FALSE}

  #PDF
 pander(ST1, caption = "Table 6.1: Summary of the available numbers of male and female mice from each strain and originating institution.")
  #HTML
    #kable(ST1, caption = "Summary of the available numbers of male and female mice from each strain and originating institution.") %>%
    #kable_styling() %>%
    #scroll_box(width = "100%", height = "200px")

@@

#PDF
pander(cbind(meta1 %>% count(parameter_group)), caption = "Table 6.2: Trait categories (parameter_group) and the number of correlated traits within these categories. Traits were meta-analysed using robumeta")

#kable(cbind(meta1 %>% count(parameter_group)), caption = "Trait categories (parameter_group) and the number of correlated traits within these categories. Traits were meta-analysed using robumeta") %>%
  #kable_styling() %>%
  #scroll_box(width = "100%", height = "200px")
```

@@

# PDF
pander(metacombo, caption = "Table 6.3: We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.  We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.")

#HTML
#kable(metacombo, digits = 3, caption = "We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.  We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.") %>%
  #kable_styling() %>%
  #scroll_box(width = "100%", height = "200px")

@@

#PDF
pander(overall2, caption = "Table 6.4: Summary of overall meta-analyses on the functional trait group level (GroupingTerm). Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.")

#HTML
#kable(overall2, digits = 3, caption = "Summary of overall meta-analyses on the functional trait group level (GroupingTerm). Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.") %>%
#kable_styling() %>%
#scroll_box(width = "100%", height = "200px")
```

@@

        #PDF
    pander(mf_sig, caption = "Table 6.5: Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex. This table summarizes findings for both sexes and the respective functional trait groups.")  
      #HTML
  #kable(mf_sig, digits = 3, caption = "Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex. This table summarizes findings for both sexes and the respective functional trait groups.") %>%
  #kable_styling() %>%
  #scroll_box(width = "100%", height = "300px")
```

@@

  # PDF
  pander(het, caption = "Table 6.6: Summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.")

  # HTML
  #kable(het, digits = 3, caption = "Summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.") %>%
   #kable_styling() %>%
    #scroll_box(width = "100%", height = "200px")

>>>>

---
title: 'Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary
  and statistical implications'
author: Susanne Zajitschek,  Felix Zajitschek, Russell Bonduriansky, Robert  Brooks,
  Will Cornwell, Daniel Falster, Malgorzata Lagisz, Jeremy Mason, Alistair Senior,
  Daniel Noble, & Shinichi Nakagawa
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    code_folding: hide
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 6
    toc_float: yes
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
  word_document:
    toc: yes
    toc_depth: '4'
  html_notebook:
    toc: yes
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '4'
  bookdown::word_document2:
    toc: yes
    toc_depth: 6
    number_sections: true
    theme: flatly
subtitle: Electronic Supplementary Material
always_allow_html: yes
---

@@

                    I2_tot <- round(sum(sigma2) / sum(sigma2 + sigmaM), digits = 3)*100
                  return(I2_tot)
      }
      results_alltraits_grouping[t, c(2:17,19:26)] <- c(f(cvr),lnCVR_I2 = extract_I2(cvr), f(cv), lnVR_I2 = extract_I2(cv), f(means), lnRR_I2 = extract_I2(means), k=means$k, male_N = sum(results$male_n_ind), female_N = sum(results$female_n_ind), min_male_N = min(results$male_n_ind), max_male_N = max(results$male_n_ind), mean_male_N = mean(results$male_n_ind),
                                                        min_female_N = min(results$female_n_ind), max_female_N = max(results$female_n_ind), mean_female_N = mean(results$female_n_ind))
      results_alltraits_grouping[t, 18]   <- unique(results$trait)
    },
    error = function(e) {
      cat("ERROR :", t, conditionMessage(e), "\n")
    }
  )
}
```

@@

```{r cleanMeta1, results = "hide"}
results_alltraits_grouping2 <- 
  results_alltraits_grouping %>%

@@

overall2 <- bind_rows(extract_trait(overall1, "Behaviour"), 
                      extract_trait(overall1, "Morphology"), 
                      extract_trait(overall1, "Metabolism"), 
                      extract_trait(overall1, "Physiology"), 
                      extract_trait(overall1, "Immunology"), 
                      extract_trait(overall1, "Hematology"), 
                      extract_trait(overall1, "Heart"), 
                      extract_trait(overall1, "Hearing"), 
                      extract_trait(overall1, "Eye"), 
                      All)

@@

# Invidual table for heterogeneity across all traits
 kable(metacombohetero,, digits = 3) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

@@

heterog4 <- bind_rows(heteroCVR.ci, heteroVR.ci, heteroRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing)

@@

overall4.male.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 

@@

plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)

@@

overall4.female.sig <- bind_rows(lnCVR.ci, lnRR.ci) %>% 

@@

overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

overall4.female.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high) # Note: bind_rows may need to be replaced by rbind

overall4.female.sigS <- overall4.female.sigS %>%
                          mutate(value = as.numeric(value),
                                 ci.low = as.numeric(ci.low),
                                 ci.high = as.numeric(ci.low))

overall4.female.sigS$label <- "CI not overlapping zero"

@@

overall4.perc <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
# may require: 	 %>% mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))

@@

overall4.male.perc <- bind_rows(lnCVR.ci,lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

@@

```{r Table1_prep, echo = FALSE, eval = TRUE, results='hide'}
#Initial checks
  #length(unique(data$parameter_name)) # 232 traits
  #length(unique(data$parameter_group)) # 161 parameter groups
 # length(unique(data$procedure_name)) # 26 procedure groups
  #length(unique(data$biological_sample_id)) # 27147 individial mice
# To show a table with number of males and females per strain per production center:
     ST1 <- cbind(data %>% 
                   group_by(production_center, strain_name) %>% 
                   count(biological_sample_id, sex) %>% 
                   count(sex) %>% 
                   print(n = Inf)) 
```

```{r Table1, message=FALSE}

  #PDF
 #pander(ST1, caption = "Table 6.1: Summary of the available numbers of male and female mice from each strain and originating institution.")
  #HTML
    kable(ST1, caption = "Summary of the available numbers of male and female mice from each strain and originating institution.") %>%
    kable_styling() %>%
    scroll_box(width = "100%", height = "200px")

@@

#PDF
#pander(cbind(meta1 %>% count(parameter_group)), caption = "Table 6.2: Trait categories (parameter_group) and the number of correlated traits within these categories. Traits were meta-analysed using robumeta")

kable(cbind(meta1 %>% count(parameter_group)), caption = "Trait categories (parameter_group) and the number of correlated traits within these categories. Traits were meta-analysed using robumeta") %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```

@@

# PDF
#pander(metacombo, caption = "Table 6.3: We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.  We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.")

#HTML
kable(metacombo, digits = 3, caption = "We use this corrected (for correlated traits) results table, which contains each of the meta-analytic means for all effect sizes of interest, for further analyses.  We further use this table as part of the Shiny App, which is able to provide the percentage differences between males and females for mean, variance and coefficient of variance.") %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

@@

#PDF
#pander(overall2, caption = "Table 6.4: Summary of overall meta-analyses on the functional trait group level (GroupingTerm). Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.")

#HTML
kable(overall2, digits = 3, caption = "Summary of overall meta-analyses on the functional trait group level (GroupingTerm). Results for lnCVR, lnVR and lnRR and their respective upper and lower 95 percent CI's, standard error and I2 values are provided.") %>%
 kable_styling() %>%
 scroll_box(width = "100%", height = "200px")
```

@@

        #PDF
    #pander(mf_sig, caption = "Table 6.5: Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex. This table summarizes findings for both sexes and the respective functional trait groups.")  
      #HTML
  kable(mf_sig, digits = 3, caption = "Provides an overview of meta-analysis results performed on traits that were significantly biased towards either sex. This table summarizes findings for both sexes and the respective functional trait groups.") %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "300px")
```

@@

  # PDF
  #pander(het, caption = "Table 6.6: Summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.")

  # HTML
  kable(het, digits = 3, caption = "Summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.") %>%
   kable_styling() %>%
    scroll_box(width = "100%", height = "200px")
